RadLib: a radiative property model library for CFD

### 2021-10-11 submissions/CPC_response_to_reviewers_revision2.md

8) In lines 562-564: "The FDS default model uses a single gray gas with a composition and temperature dependent
   absorption coefficient computed from RADCAL." Is this equivalent to the PM model in RadLib? If so, a comparison with
   PM from RadLib and FDS default will be a good validation. Also, what RTE solver does FDS default use?

   **No, they are not equivalent. FDS uses the RadCal narrow-band model that depends on a user-specified radiative path length with a default value of 0.1 m. This is a geometry-dependent property that is different than a PM coefficient. For the radiative solver, FDS uses a finite-volume discrete ordinates RTE solver. That is noted in the paper in the first paragraph of Section 5.1. We added a note of the path length variable in the revised manuscript.**
</font>

9) In Section 5.2 can the author comment on the computational cost of RadLib-coupled FDS runs? Some quantitative
   information on the computational cost of using RadLib for a coupled run will be very useful. For example, the authors
   can compare the cost of the same FDS configuration simulated without any radiation, with RadLib, and with the
   FDS-default model.

   **FDS simulations were rerun. The cost of the FDS simulations relative to the FDS default radiative case is 1, 1.68, and 1.71, for the default, WSGG, and RCSLW, respectively. This has been added to the paper with a note that the small difference between the WSGG and RCSLW costs imply that the cost is dominated by the solver rather than the property model. The corresponding results plots were updated.**

### 2021-10-18 manuscript/manuscript.tex
DOL: accepting VBS edits, deleting commented old version

\begin{abstract}
RadLib is a C++ library of radiation property models that can be applied to variety of systems involving radiative heat transfer, including CFD simulations. RadLib includes three major radiation property models---Planck Mean (PM) absorption coefficients, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model. RadLib includes C++, Python, and Fortran interfaces and can be expanded to include additional models. Several example cases illustrate use of the models with an included ray-tracing solver, compare their accuracy relative to line-by-line (LBL) solutions, and examine their computational costs. Additionally, an integrated CFD example of an ethylene burner configuration using Fire Dynamics Simulator (FDS) is provided.
%Several example cases illustrate the use of the models with an included ray-tracing solver and compare them in terms of accuracy relative to line-by-line solutions. A CFD example is provided of an ethylene burner in a compartment using Fire Dynamics Simulator (FDS). The computational cost of the models is compared.
RadLib provides researchers with convenient access to validated radiation property models and a framework for further development.
\end{abstract}

@@

Modeling radiative heat transfer in participating media in high temperature systems is a challenging problem. Combustion is one of the key radiative transfer applications, and combustion CFD is uniquely challenging because it involves numerous tightly coupled physical phenomena---including multicomponent mass transfer, convective and radiative heat transfer, turbulent fluid dynamics, multi-phase and particle flows, and complex chemical reaction kinetics---that span many orders of magnitude in both length and time scales.
Accurate radiation modeling often complicates combustion simulations because it can be difficult to implement and computationally expensive relative to the overall simulation cost.
%Combustion simulations are often complicated by a lack of accurate radiation modeling, which can be difficult to implement and computationally expensive relative to overall simulation cost.
Radiative heat transfer modeling in combustion systems is frequently neglected or oversimplified, resulting in significant errors flame temperatures~\citep{Modest_2016}.
%Frequently, radiative heat transfer modeling in combustion systems is either neglected or oversimplified, resulting in significant errors flame temperatures~\citep{Modest_2016}.
Additionally, some late-stage flame phenomena, particularly soot behavior and flame sheet breakthrough, increasingly depend on and influence the magnitude of radiative heat losses and are difficult to simulate accurately without robust radiation modeling \cite{Modest_2013}. These problems motivated development of the RadLib library, which implements three radiation property models with C++, Python, and Fortran interfaces and provides a framework for additional models and further development, giving researchers convenient access to advanced radiation property modeling tools.

The core mechanisms of radiative phenomena are physically and mathematically complex.
Unlike other modes of heat transfer, radiation is governed by the radiative transfer equations (RTE), a set of integro-differential equations that depend on both direction and wavelength.
%Unlike other modes of heat transfer, radiation is governed by a set of integro-differential equations that depend on both direction and wavelength, known as the radiative transfer equations (RTE).
Computational radiation solvers require two distinct but interconnected parts: (1) a solution approach for the radiative transfer equations (RTE) and (2) a radiative property model. The complexity, implementation, and computational cost of these two parts can vary widely depending on the models chosen.
For example, the optically thin approximation for solution of the RTE is trivial, while the discrete ordinates model (DOM) and reverse Monte Carlo ray tracing (RMCRC) model, among others, are significantly more involved.
%The optically thin model for solution of the RTE is trivial, while the discrete ordinates model (DOM) and reverse Monte Carlo ray tracing (RMCRC) model, among others, are significantly more involved.
Similarly, radiation property models range from simple correlations for computing mean absorption coefficients to gray gas models, including the weighted sum of gray gases (WSGG) model, to more advanced spectral line-weighted-sum-of-gray-gases (SLW) models to full line-by-line (LBL) treatment.
In practical engineering simulations, the solution of the RTE is often the most complex and costly part of radiative simulation, but advanced property models such as the Rank Correlated SLW (RCSLW) model, discussed in Section~\ref{s:RCSLW}, are nontrivial to understand, implement, and validate.
%In practical engineering simulations, the solution of the RTE is often the most complex and costly part of radiative simulation, but advanced property models such as the Rank Correlated SLW (RCSLW), discussed here, are nontrivial models to understand, implement, and validate.
RadLib addresses the second part of the radiation solver requirements by providing a set of implemented and validated radiation property models that can be applied alongside various solution approaches for the RTE.
%RadLib addresses this second radiative property model part of radiation simulation by providing a set of implemented and validated radiation property models that can be applied to various solution approaches for the RTE.

For an absorbing, emitting, and non-scattering medium (considered here), the RTE solved for the intensity $I$ at a specified wavenumber $\eta$ in unit direction $\mathbf{s}$ is described by
%For an absorbing, emitting, and non-scattering medium (considered here), the RTE for intensity $I$ at a specified wavenumber $\eta$ in unit direction $\mathbf{s}$ is described by
%
\begin{linenomath}
\begin{equation} \label{e:RTE_general}
    \frac{dI_{\eta}}{ds} = -\kappa_{\eta}I_{\eta} + \kappa_{\eta}I_{b,\eta},
\end{equation}
\end{linenomath}
%
where $I_{\eta}$ is the spectral radiative intensity, $I_{b,\eta}$ is the blackbody spectral radiative intensity (or Planck function), $\kappa_{\eta}$ is the spectral absorption coefficient of the medium, and $s$ is a path length along direction $\mathbf{s}$.
%where $I_{\eta}$ is the radiative spectral intensity, $I_{b,\eta}$ is the spectral blackbody radiative intensity (or Planck function), $\kappa_{\eta}$ is the spectral absorption coefficient of the medium, and $s$ is a path length along direction $\mathbf{s}$.
Solving the RTE requires information about the radiative properties of the materials and media in the system. Radiative property data typically take the form of radiation absorption coefficients $\kappa$, which are provided by a radiation property model. Gas absorption spectra consist of millions of spectral lines corresponding to the individual quantum mechanical energy levels of gas molecules and depend on the local thermochemical state of the system (e.g., temperature, pressure, and composition).
Radiation property models are typically developed as correlations from high-resolution spectral databases, reducing the huge amount of spectral data contained in those databases and simplifying the evaluation of absorption coefficients \cite{Zhang_2002b}.

The direct solution of the spectral RTE using so-called line-by-line (LBL) calculations, in which the RTE is solved for each individual spectral line, is computationally prohibitive for most practical configurations and used primarily for model validation.
%The direct solution of the spectral RTE using so-called line-by-line calculations, in which the RTE is solved for each individual spectral line, is computationally prohibitive for most practical configurations and is used primarily for model validation.
Simple band models rely on estimated or averaged line-of-sight property values that cannot be directly incorporated into the RTE.
%Some band models rely on estimated or averaged "line-of-sight" property values that cannot be directly incorporated into the RTE.
%dol
Modern band models require high-resolution databases and reorder emission levels rather than averaging across sequential absorption bands, but these can lose accuracy when applied to nonhomogeneous media and may still require large numbers of RTE evaluations \citep{Modest_2016}.

Global models are an important class of radiation property models that use spectrally-integrated radiation properties \cite{Hottel_1967,Modest_2013,Modest_2016}.
Assuming spectrally uniform (gray) properties over a wavenumber region $j$, we can integrate Eq.~\ref{e:RTE_general} over a set of fixed wavenumber ranges $\eta_j$ to obtain
%Assuming spectrally uniform (gray) properties over a wavenumber region $j$, we can integrate Eq.~\ref{e:RTE_general} over the fixed wavenumber ranges $\eta_j$ to obtain
%
\begin{linenomath}
\begin{equation} \label{e:RTE_wsgg}
    \frac{dI_j}{ds} = -\kappa_jI_j + a_j\kappa_jI_b, \hspace{20pt} j=0,1,...,n,
\end{equation}
\end{linenomath}
%
where $I_b$ is the total blackbody intensity, $I_j$ is the total radiative intensity in the region defined by gray gas $j$, $\kappa_j$ is the spectrally integrated absorption coefficient for gray gas $j$, and $a_j$ is a weighting factor defined by
%where $I_b$ is the blackbody intensity, $I_j$ is the radiative intensity in the region defined by gray gas $j$, $\kappa_j$ is the spectrally integrated absorption coefficient for gray gas $j$, and $a_j$ is a weighting factor defined by
%
\begin{linenomath}
\begin{align}
    &a_j= \frac{\int_{\eta_j}I_{b,\eta}d\eta}{I_b},\\
    &\sum_j a_j = 1.
\end{align}
\end{linenomath}
%
Given spatial profiles of $\kappa_j$ and $a_j$, Eq.~\ref{e:RTE_wsgg} can be evaluated for each of the $n$ gray gases. Normally, an additional ``clear gas'', $j=0$, is included to represent transparent windows in the spectrum for which $\kappa_0=0$.
%Given spatial profiles of $\kappa_j$ and $a_j$, Eq.~\ref{e:RTE_wsgg} can be evaluated for each of the $n$ gray gases. Normally, an additional ``clear gas'', $j=0$, is included that represents transparent windows in the spectrum for which $\kappa_0=0$.
This gray gas approach allows calculation of the total radiative intensity $I$ by summing the individual gray gas intensities:
%This gray gas approach allows calculation of the total radiative intensity $I$ by summing the individual gray gas:
%
\begin{linenomath}
\begin{equation}
I=\int_{\eta=0}^{\infty}I_{\eta}d\eta=\sum_{j=1}^n I_j.
\end{equation}
\end{linenomath}
%

The heat flux $\mathbf{q}$ (in units of kW/m$^2$) and volumetric radiative heat source $Q$ (kW/m$^3$) can be calculated by integrating over directional solid angles ($\mathbf{s}\Omega$) on the sphere and finding the divergence of the resulting vector field, respectively:
%The heat flux $\mathbf{q}$ (in units of kW/m$^2$) and volumetric radiative heat source $Q$ (kW/m$^3$) can be calculated by integrating over directional solid angles ($\mathbf{s}\Omega$) on the sphere and finding the divergence of the resulting vector field,
%
\begin{linenomath}
\begin{equation}
    \mathbf{q} = \int_{4\pi}I(\mathbf{s})\mathbf{s}d\Omega.
\end{equation}
\end{linenomath}
%
\begin{linenomath}
\begin{equation}
    Q = -\nabla\cdot\mathbf{q}.
\end{equation}
\end{linenomath}
%
Global models are especially attractive in computational heat transfer applications because they can provide good accuracy while limiting computational costs.

@@

At present, RadLib includes three radiation property models of varying complexity: a Planck Mean (PM) absorption coefficients model, a weighted sum of gray gases (WSGG) model, and the rank-correlated spectral line-weighted-sum-of-gray-gases (RCSLW) model.
%At present, RadLib includes three radiation property models of varying complexity: Planck Mean absorption coefficients, most often applied alongside the optically thin approximation, a weighted sum of gray gases (WSGG) model, and the rank-correlated spectral line-weighted-sum-of-gray-gases (RCSLW) model.
These models were chosen for their relevance to practical radiative heat transfer simulations. They represent increasing levels of complexity, computational cost, and accuracy. Each model is discussed in more detail in the following sections.

@@

The version of the PM model implemented in RadLib comes from the Turbulent Nonpremixed Flames (TNF) workshop \cite{TNF}, a long-running collaboration between experimental and computational researchers in turbulent combustion \citep{Smith_2003,Barlow_2001}. The workshop includes a number of laboratory jet flames that have been extensively characterized\textemdash including temperature, velocity, and composition profiles\textemdash and serve as target flames against which computational scientists can validate models and simulations.
%The particular version of the model implemented is from the Turbulent Nonpremixed Flames (TNF) workshop \cite{TNF}. This is a long-running collaboration between experimental and computational researchers in turbulent combustion \citep{Smith_2003,Barlow_2001}. The workshop includes a number of laboratory jet flames that have been extensively researched for flame temperature, velocity, and composition profiles, and these serve as target flames for computational scientists to validate simulations and models.
The PM model implemented in RadLib is the model advocated by the TNF workshop and, as a result, widely used in turbulent combustion research.
%The PM model implemented here is the one advocated (and hence widely used) by the TNF workshop.
For each chemical species considered, the PM model provides the absorption coefficient as a fourth or fifth order polynomial fit in one of two temperature ranges to $\kappa(T)$ values computed from the RADCAL database \cite{Grosshandler_1993}.
%For each species, the PM model provides the absorption coefficient as a fourth or fifth order polynomial fit in one of two temperature ranges to $\kappa(T)$ values computed from the RADCAL database \cite{Grosshandler_1993}.
The model accommodates temperatures between 300 K and 2500 K and considers the chemical species \ce{CO2}, \ce{H2O}, \ce{CO}, \ce{CH4}.
%The model accommodates temperatures between 300 K and 2500 K. See \cite{TNF} for details and references. The PM model here considers the species \ce{CO2}, \ce{H2O}, \ce{CO}, \ce{CH4}.
\ce{CO}, \ce{CH4} contribute significantly less to radiative absorption and emission than \ce{CO2} and \ce{H2O}, but the TNF Workshop radiation model includes them because \ce{CH4} and syngas (which consists of \ce{CO} and \ce{H2}) are common fuels in combustion applications and so are present in high concentrations in the fuel streams of several TNF target flames. Additionally, \ce{CO} is also a common species in rich flame regions and is also included in the RCSLW model.
%The last two species have lower absorption than the first two, but are included because \ce{CH4} and syngas (consisting of \ce{CO} and \ce{H2}) are common fuels in combustion applications and so are present in the TNF flames in high concentrations in the fuel stream. (\ce{CO} is also a common species in rich flame regions and is also included in the RCSLW model.)

The PM model is not as accurate as the other two models considered, as illustrated by the example cases in Section~\ref{s:discussion}.
%The PM model is not as accurate as the other two models considered, and this is illustrated in Section~\ref{s:discussion}.
It is implemented in RadLib primarily for comparison and evaluation against other radiation property models because of its relatively common use in combustion simulations.
%It is implemented in RadLib primarily for comparison and evaluation against other radiation property models because of its relatively common use in some simulations.
The PM model reportedly overpredicts radiative losses and underpredicts flame temperature by as much as 100 K or more \cite{Frank_2000,Zhu_2002,Coelho_2002}, though this depends strongly on the geometric configuration of the simulation.
%The model has been reported to overpredict radiative losses and underpredict flame temperature by as much as 100 K or more \cite{Frank_2000,Zhu_2002,Coelho_2002}, though this will depend strongly on the geometric configuration.
Accurate results have been reported for hydrogen jet flames \cite{Barlow_1999}.

The PM model is most often used in conjunction with the optically thin approximation for solving the RTE, in which case the radiative source term of the energy transport equation reduces to an algebraic expression and the overall computational cost of the radiative treatment is negligible in comparison to other aspects of reacting flow simulations. Many smaller combustion configurations are radiatively thin and experience minimal radiative heat loss; non-sooting laboratory-scale research jet flames, for example, tend to exhibit radiative losses of around 5\%. At low levels of radiative heat loss, the accuracy of the radiation model is not as crucial, and simpler radiative property models like the PM model may be appropriate.
%The PM model is often used in conjunction with the optically-thin approximation for solving the RTE, in which case the radiative source term of the energy transport equation is particularly simple, and the overall computational cost of the radiative treatment is negligible in comparison to other aspects of a reacting flow simulation. Many smaller combustion applications are radiatively thin, and have smaller radiative heat loss. It is not uncommon for non-sooting laboratory-scale research jet flames to have radiative losses of around 5\%. At these levels, the accuracy of the radiative property model is not as crucial, and simpler models like the PM model are appropriate.

@@

For multicomponent gas mixtures, the mixture absorption cross section $C_{\eta}$ is defined as a weighted sum of its component absorption cross sections \cite{Solovjov_2000}.
In RadLib, the RCSLW implementation considers \ce{H2O}, \ce{CO2}, and \ce{CO}, for which the mixture absorption cross section for a given gray gas is given by
%The RCSLW implementation considers \ce{H2O}, \ce{CO2}, and \ce{CO}, for which the mixture absorption cross section for a given gray gas is given by
%
\begin{linenomath}
\begin{equation} \label{e:multiC}
C_{\eta} = x_{\ce{CO2}}C_{\ce{CO2},\eta} + x_{\ce{H2O}}C_{\ce{H2O},\eta} + x_{\ce{CO}}C_{\ce{CO},\eta},
\end{equation}
\end{linenomath}
%
where $x$ denotes mole fraction.
Assuming that the absorption cross sections of each species are statistically independent, the mixture ALBDF for a given gray gas can be computed using the multiplication method \cite{Solovjov_2000}:
%
\begin{linenomath}
\begin{equation} \label{e:multiF}
F_{\eta}(C_{\eta}) = F_{\ce{CO2},\eta} \left( \frac{C_{\eta}}{x_{\ce{CO2}}} \right) F_{\ce{H2O},\eta} \left( \frac{C_{\eta}}{x_{\ce{H2O}}} \right) F_{\ce{CO},\eta} \left( \frac{C_{\eta}}{x_{\ce{CO}}} \right).
\end{equation}
\end{linenomath}
%
Note that the $\BS{\phi}$ and $T$ arguments of $F$ are omitted from Eq.~\ref{e:multiF} for clarity.
%Here, the $\BS{\phi}$ and $T$ arguments of $F$ are omitted from Eq.~\ref{e:multiF} for clarity.

>>>>

\begin{abstract}
RadLib is a C++ library of radiation property models that can be applied to variety of systems involving radiative heat transfer, including CFD simulations. RadLib includes three major radiation property models---Planck Mean (PM) absorption coefficients, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model. RadLib includes C++, Python, and Fortran interfaces and can be expanded to include additional models. Several example cases illustrate use of the models with an included ray-tracing solver, compare their accuracy relative to line-by-line (LBL) solutions, and examine their computational costs. Additionally, an integrated CFD example of an ethylene burner configuration using Fire Dynamics Simulator (FDS) is provided.
RadLib provides researchers with convenient access to validated radiation property models and a framework for further development.
\end{abstract}

@@

Modeling radiative heat transfer in participating media in high temperature systems is a challenging problem. Combustion is one of the key radiative transfer applications, and combustion CFD is uniquely challenging because it involves numerous tightly coupled physical phenomena---including multicomponent mass transfer, convective and radiative heat transfer, turbulent fluid dynamics, multi-phase and particle flows, and complex chemical reaction kinetics---that span many orders of magnitude in both length and time scales.
Accurate radiation modeling often complicates combustion simulations because it can be difficult to implement and computationally expensive relative to the overall simulation cost.
Radiative heat transfer modeling in combustion systems is frequently neglected or oversimplified, resulting in significant errors flame temperatures~\citep{Modest_2016}.
Additionally, some late-stage flame phenomena, particularly soot behavior and flame sheet breakthrough, increasingly depend on and influence the magnitude of radiative heat losses and are difficult to simulate accurately without robust radiation modeling \cite{Modest_2013}. These problems motivated development of the RadLib library, which implements three radiation property models with C++, Python, and Fortran interfaces and provides a framework for additional models and further development, giving researchers convenient access to advanced radiation property modeling tools.

The core mechanisms of radiative phenomena are physically and mathematically complex.
Unlike other modes of heat transfer, radiation is governed by the radiative transfer equation (RTE), an integro-differential equation that depend on both direction and wavelength.
Computational radiation solvers require two distinct but interconnected parts: (1) a solution approach for the radiative transfer equations (RTE) and (2) a radiative property model. The complexity, implementation, and computational cost of these two parts can vary widely depending on the models chosen.
For example, the optically thin approximation for solution of the RTE is trivial, while the discrete ordinates model (DOM) and reverse Monte Carlo ray tracing (RMCRC) model, among others, are significantly more involved.
Similarly, radiation property models range from simple correlations for computing mean absorption coefficients to gray gas models, including the weighted sum of gray gases (WSGG) model, to more advanced spectral line-weighted-sum-of-gray-gases (SLW) models to full line-by-line (LBL) treatment.
In practical engineering simulations, the solution of the RTE is often the most complex and costly part of radiative simulation, but advanced property models such as the Rank Correlated SLW (RCSLW) model, discussed in Section~\ref{s:RCSLW}, are nontrivial to understand, implement, and validate.
RadLib addresses the second part of the radiation solver requirements by providing a set of implemented and validated radiation property models that can be applied alongside various solution approaches for the RTE.

For an absorbing, emitting, and non-scattering medium (considered here), the RTE solved for the intensity $I$ at a specified wavenumber $\eta$ in unit direction $\mathbf{s}$ is described by
%
\begin{linenomath}
\begin{equation} \label{e:RTE_general}
    \frac{dI_{\eta}}{ds} = -\kappa_{\eta}I_{\eta} + \kappa_{\eta}I_{b,\eta},
\end{equation}
\end{linenomath}
%
where $I_{\eta}$ is the spectral radiative intensity, $I_{b,\eta}$ is the blackbody spectral radiative intensity (or Planck function), $\kappa_{\eta}$ is the spectral absorption coefficient of the medium, and $s$ is a path length along direction $\mathbf{s}$.
Solving the RTE requires information about the radiative properties of the materials and media in the system. Radiative property data typically take the form of radiation absorption coefficients $\kappa$, which are provided by a radiation property model. Gas absorption spectra consist of millions of spectral lines corresponding to the individual quantum mechanical energy levels of gas molecules and depend on the local thermochemical state of the system (e.g., temperature, pressure, and composition).
Radiation property models are typically developed as correlations from high-resolution spectral databases, reducing the huge amount of spectral data contained in those databases and simplifying the evaluation of absorption coefficients \cite{Zhang_2002b}.

The direct solution of the spectral RTE using so-called line-by-line (LBL) calculations, in which the RTE is solved for each individual spectral line, is computationally prohibitive for most practical configurations and used primarily for model validation.
Simple band models rely on estimated or averaged line-of-sight property values that cannot be directly incorporated into the RTE.
Modern band models require high-resolution databases and reorder emission levels rather than averaging across sequential absorption bands, but these can lose accuracy when applied to nonhomogeneous media and may still require large numbers of RTE evaluations \citep{Modest_2016}.

Global models are an important class of radiation property models that use spectrally-integrated radiation properties \cite{Hottel_1967,Modest_2013,Modest_2016}.
Assuming spectrally uniform (gray) properties over a wavenumber region $j$, we can integrate Eq.~\ref{e:RTE_general} over a set of fixed wavenumber ranges $\eta_j$ to obtain
%
\begin{linenomath}
\begin{equation} \label{e:RTE_wsgg}
    \frac{dI_j}{ds} = -\kappa_jI_j + a_j\kappa_jI_b, \hspace{20pt} j=0,1,...,n,
\end{equation}
\end{linenomath}
%
where $I_b$ is the total blackbody intensity, $I_j$ is the total radiative intensity in the region defined by gray gas $j$, $\kappa_j$ is the spectrally integrated absorption coefficient for gray gas $j$, and $a_j$ is a weighting factor defined by
%
\begin{linenomath}
\begin{align}
    &a_j= \frac{\int_{\eta_j}I_{b,\eta}d\eta}{I_b},\\
    &\sum_j a_j = 1.
\end{align}
\end{linenomath}
%
Given spatial profiles of $\kappa_j$ and $a_j$, Eq.~\ref{e:RTE_wsgg} can be evaluated for each of the $n$ gray gases. Normally, an additional ``clear gas'', $j=0$, is included to represent transparent windows in the spectrum for which $\kappa_0=0$.
This gray gas approach allows calculation of the total radiative intensity $I$ by summing the individual gray gas intensities:
%
\begin{linenomath}
\begin{equation}
I=\int_{\eta=0}^{\infty}I_{\eta}d\eta=\sum_{j=1}^n I_j.
\end{equation}
\end{linenomath}
%

The heat flux $\mathbf{q}$ (in units of kW/m$^2$) and volumetric radiative heat source $Q$ (kW/m$^3$) can be calculated by integrating over directional solid angles ($\mathbf{s}\Omega$) on the sphere and finding the divergence of the resulting vector field, respectively:
%
\begin{linenomath}
\begin{equation}
    \mathbf{q} = \int_{4\pi}I(\mathbf{s})\mathbf{s}d\Omega.
\end{equation}
\end{linenomath}
%
\begin{linenomath}
\begin{equation}
    Q = -\nabla\cdot\mathbf{q}.
\end{equation}
\end{linenomath}
%
Global models are especially attractive in computational heat transfer applications because they can provide good accuracy while limiting computational costs.

@@

At present, RadLib includes three radiation property models of varying complexity: a Planck Mean (PM) absorption coefficients model, a weighted sum of gray gases (WSGG) model, and the rank-correlated spectral line-weighted-sum-of-gray-gases (RCSLW) model.
These models were chosen for their relevance to practical radiative heat transfer simulations. They represent increasing levels of complexity, computational cost, and accuracy. Each model is discussed in more detail in the following sections.

@@

The version of the PM model implemented in RadLib comes from the Turbulent Nonpremixed Flames (TNF) workshop \cite{TNF}, a long-running collaboration between experimental and computational researchers in turbulent combustion \citep{Smith_2003,Barlow_2001}. The workshop includes a number of laboratory jet flames that have been extensively characterized\textemdash including temperature, velocity, and composition profile measurements\textemdash and serve as target flames against which models and simulations can be validated. 
The PM model implemented in RadLib is the model advocated by the TNF workshop and, as a result, widely used in turbulent combustion research.
For each chemical species considered, the PM model provides the absorption coefficient as a fourth or fifth order polynomial fit in one of two temperature ranges to $\kappa(T)$ values computed from the RADCAL database \cite{Grosshandler_1993}.
The model accommodates temperatures between 300 K and 2500 K and considers the chemical species \ce{CO2}, \ce{H2O}, \ce{CO}, \ce{CH4}.
\ce{CO} and \ce{CH4} contribute significantly less to radiative absorption and emission than \ce{CO2} and \ce{H2O}, but the TNF Workshop radiation model includes them because \ce{CH4} and syngas (which consists of \ce{CO} and \ce{H2}) are common fuels in combustion applications and so are present in high concentrations in the fuel streams of several TNF target flames. \ce{CO} is also a common species in rich flame regions and is also included in the RCSLW model.

The PM model is not as accurate as the other two models considered, as illustrated by the example cases in Section~\ref{s:discussion}.
It is implemented in RadLib primarily for comparison and evaluation against other radiation property models because of its relatively common use in combustion simulations.
The PM model reportedly overpredicts radiative losses and underpredicts flame temperature by as much as 100 K or more \cite{Frank_2000,Zhu_2002,Coelho_2002}, though this depends strongly on the geometric configuration of the simulation.
Accurate results have been reported for hydrogen jet flames \cite{Barlow_1999}.

The PM model is most often used in conjunction with the optically thin approximation for solving the RTE, in which case the radiative source term of the energy transport equation reduces to an algebraic expression and the overall computational cost of the radiative treatment is negligible in comparison to other aspects of reacting flow simulations. Many smaller combustion configurations are radiatively thin and experience low radiative heat loss; non-sooting laboratory-scale research jet flames, for example, tend to exhibit radiative losses of around 5\%. At low levels of radiative heat loss, the accuracy of the radiation model is not as crucial, and simpler radiative property models like the PM model may be appropriate.

@@

For multicomponent gas mixtures, the mixture absorption cross section $C_{\eta}$ is defined as a weighted sum of its component absorption cross sections \cite{Solovjov_2000}.
In RadLib, the RCSLW implementation considers \ce{H2O}, \ce{CO2}, and \ce{CO}, for which the mixture absorption cross section for a given gray gas is given by
%
\begin{linenomath}
\begin{equation} \label{e:multiC}
C_{\eta} = x_{\ce{CO2}}C_{\ce{CO2},\eta} + x_{\ce{H2O}}C_{\ce{H2O},\eta} + x_{\ce{CO}}C_{\ce{CO},\eta},
\end{equation}
\end{linenomath}
%
where $x$ denotes mole fraction.
Assuming that the absorption cross sections of each species are statistically independent, the mixture ALBDF for a given gray gas can be computed using the multiplication method \cite{Solovjov_2000}:
%
\begin{linenomath}
\begin{equation} \label{e:multiF}
F_{\eta}(C_{\eta}) = F_{\ce{CO2},\eta} \left( \frac{C_{\eta}}{x_{\ce{CO2}}} \right) F_{\ce{H2O},\eta} \left( \frac{C_{\eta}}{x_{\ce{H2O}}} \right) F_{\ce{CO},\eta} \left( \frac{C_{\eta}}{x_{\ce{CO}}} \right).
\end{equation}
\end{linenomath}
%
Note that the $\BS{\phi}$ and $T$ arguments of $F$ are omitted from Eq.~\ref{e:multiF} for clarity.
